Supplementary Material

### 2023-06-21 supplementary_file.Rmd
Second revision

# Inter-coder agreement

Out of the 25 papers selected to carry out independent double-coding, 21 had primary data available for one or more meta-analyses selected under the criteria explained in the main manuscript. Some disagreements or coding errors in the primary data were found in `r length(datasets_wo_error) - sum(datasets_wo_error)` (`r sprintf("%0.0f%%", round((1-mean(datasets_wo_error))*100,2))`) cases.  The intraclass correlation coefficient between the values coded by each coder was computed for each of those 21 datasets. The ICC values varied between `r round(min(icc_table$ICC), 3)` and `r max(icc_table$ICC)` (mean = `r round(mean(icc_table$ICC), 3)`). Full results of the inter-coder agreement are presented in Table S1.

@@

# Sensitivity analysis using other possible criteria

In the first stage, a cut-off point of 5% discrepancy between reported and reproduced results was set to screen meta-analyses. In Figure S1 this criterion is compared with other possibilities in absolute value. Figure S1 shows that the criterion used is one of the most liberal of those compared. Due to our design, the stage where the criterion was applied is only an initial screening, so the meta-analyses labelled by this criterion were reviewed at later stages in a qualitative way. Therefore, a more liberal criterion (minimizing false negatives, but increasing false positives) is more suitable. This criteria has the limitations of any relative index, but due to the mix of metrics included, it is also considered more appropriate.

@@

# Data availability over years

@@

kbl(
  log_reg_results,
  format = "latex",
  booktabs = TRUE,
  linesep = '\\addlinespace',
  col.names = c("Level", "Before 10s exclusion", "Slope", "OR", "OR LL", "OR UL", "$p$"),
  align = c("l", "l", "l","l", "l", "l","l"),
  caption = "Binary logistic regression models results",
  escape = FALSE
  ) %>% 
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  column_spec(2, width = "2cm")

```
\pagebreak
Based on the results of the four models, there seems to be an association between the publication year and the possibility of retrieving primary data from a meta-analysis. We found that all 4 ORs computed were > 1, indicating a higher probability of retrieving data the more recent the publication year of the meta-analysis. Additionally, in only one of the cases (paper-level model without excluding cases published before 2010) did the 95%CI of the OR include a value < 1.
\pagebreak

>>>>

```
# Inter-coder agreement 
Out of the 25 papers selected to carry out independent double-coding, 21 had primary data available for one or more meta-analyses selected under the criteria explained in the main manuscript. Some disagreements or coding errors in the primary data were found in `r length(datasets_wo_error) - sum(datasets_wo_error)` (`r sprintf("%0.0f%%", round((1-mean(datasets_wo_error))*100,2))`) cases.  The intraclass correlation coefficient between the values coded by each coder was computed for each of those 21 datasets. The ICC values varied between `r round(min(icc_table$ICC), 3)` and `r max(icc_table$ICC)` (mean = `r round(mean(icc_table$ICC), 3)`). Full results of the inter-coder agreement are presented in Table S1.

@@

# Sensitivity analysis using other possible criteria
In the first stage, a cut-off point of 5% discrepancy between reported and reproduced results was set to screen meta-analyses. In Figure S1 this criterion is compared with other possibilities in absolute value. Figure S1 shows that the criterion used is one of the most liberal of those compared. Due to our design, the stage where the criterion was applied is only an initial screening, so the meta-analyses labelled by this criterion were reviewed at later stages in a qualitative way. Therefore, a more liberal criterion (minimizing false negatives, but increasing false positives) is more suitable. This criteria has the limitations of any relative index, but due to the mix of metrics included, it is also considered more appropriate.

@@

# Data availability over years
\textcolor{blue}{The publication year range of the included meta-analyses in our study is quite extensive. The initial pool, from which we randomly selected a sample, comprised meta-analytic reports published between 2000 and 2020, encompassing a span of two decades. For our analysis, we focused on a random sample of 100 of these meta-analytic reports.  From the 100 included reports, 217 independent meta-analyses were selected following the criteria explained in the ‘Identification and selection of articles and meta-analyses’ section of the main paper. These meta-analyses were published between} `r min(df_mas_pyear1$publication_year)` and `r max(df_mas_pyear1$publication_year)` (`r sprintf("mean = %0.2f; sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f", mean(df_mas_pyear1$publication_year), sd(df_mas_pyear1$publication_year), median(df_mas_pyear1$publication_year), quantile(df_mas_pyear1$publication_year)[2], quantile(df_mas_pyear1$publication_year)[3])`). \textcolor{blue}{As an unrestricted random sample, the publication year distribution is clearly left-skewed, with} `r sprintf("%0.1f%%", (nrow(subset(df_mas_pyear1, publication_year >= 2010))/nrow(df_mas_pyear1))*100)` \textcolor{blue}{of the included meta-analyses published between 2010 and 2020 (see Figure 2 of the main paper for the full distribution).}

\textcolor{blue}{As shown in the main paper (see Figure 3a), there appears to be an improvement in the rate of data availability over the years. The overall data availability rate for the full sample was found to be 67\%. However, when examining meta-analyses published within specific time periods, the rates varied. For meta-analyses published between 2000 and 2010, the data availability rate was 41\%. For those published between 2011 and 2015, the rate increased to 59\%. Notably, meta-analyses published between 2016 and 2020 exhibited the highest data availability rate of 80\%. These findings suggest a positive trend of improved data availability in more recent years.}

@@

kbl(
  log_reg_results,
  format = "latex",
  booktabs = TRUE,
  linesep = '\\addlinespace',
  col.names = c("Level", "Before 10s exclusion", "Slope", "OR", "OR LL", "OR UL", "$p$", "Pertecenage change"),
  align = c("l", "l", "l","l", "l", "l","l", "l"),
  caption = "Binary logistic regression models results",
  escape = FALSE
  ) %>% 
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  column_spec(c(1, 2, 8), width = "2cm")

```
\pagebreak
Based on the results of the four models, there seems to be an association between the publication year and the possibility of retrieving primary data from a meta-analysis. We found that all 4 ORs computed were > 1, indicating a higher probability of retrieving data the more recent the publication year of the meta-analysis. \textcolor{blue}{Specifically, the odds increased from 11.85\% to 34.46\% per year.}Additionally, in only one of the cases (paper-level model without excluding cases published before 2010) did the 95%CI of the OR include a value < 1.
\pagebreak
